### 2018-06-04 CS761-RandomizedAlgorithms/assignments/a1.tex
finished a1

\documentclass[letterpaper,12pt,oneside,onecolumn]{article}
\usepackage[margin=1in, bottom=1in, top=1in]{geometry} %1 inch margins
\usepackage{amsmath, amssymb, amstext}
\usepackage{fancyhdr}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{theorem}
\usepackage{tikz}
\usepackage{tkz-berge}

%Macros
\newcommand{\A}{\mathbb{A}} \newcommand{\C}{\mathbb{C}}
\newcommand{\D}{\mathbb{D}} \newcommand{\F}{\mathbb{F}}
\newcommand{\N}{\mathbb{N}} \newcommand{\R}{\mathbb{R}}
\newcommand{\T}{\mathbb{T}} \newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}

@@

(Collaboration with Sharat, Harry and Logan)

@@

Pr(Y > 1+\epsilon) &= Pr(e^{tY}> e^{t(1+\epsilon)} \\

@@

We remove all edges incident to $s_i$ when we do not delete all edges on some $s_i-t_j$ path for some $j$. For all edges on some $s_i-t_j$ path to be preserved, necessarily $v_{s_i}$ and $v_{t_j}$ lie in the same region. Since $v_{s_i}$ and $v_{t_j}$ are orthogonal the probability they are not separated by some $r_\ell$ is 
$$1- \frac{\pi}{2}\frac{1}{\pi} = \frac{1}{2}.$$
So the probability they not separated by any $r_\ell$ is

@@

Now there are at most $\Delta$ sinks $t_j$ incident on $s_i$ and so we have
$$Pr(\text{delete all edges on $s_i$}) \leq \sum_{j=1}^tPr(\text{$s_i-t_j$ path survives}) \leq \frac{\Delta}{2^t}$$

@@

Let $X$ be a random variable counting the number of edges removed. Let $X_{ij}^1$ be an indicator variable indicating that $ij$ is removed in the first phase. Let $X_{s_i}^2$ be an indicator variable indicating that all edges incident to $s_i$ are removed in the second phase.
E[X] &= \sum_{ij \in E} Pr(X^1_{ij}) + \sum_{ij\in E} Pr(X^2_{s_i}) \\
&= \sum_{ij \in E} t\sqrt{1-v_iv_j} + \sum_{s_i} Pr(X^2_{s_i}) \\
&=

>>>>

\documentclass[letterpaper,12pt,oneside,onecolumn]{article}
\usepackage[margin=1in, bottom=1in, top=1in]{geometry} %1 inch margins
\usepackage{amsmath, amssymb, amstext}
\usepackage{fancyhdr}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{theorem}
\usepackage{tikz}
\usepackage{tkz-berge}
\usepackage{bbm}
%Macros
\newcommand{\A}{\mathbb{A}} \newcommand{\C}{\mathbb{C}}
\newcommand{\D}{\mathbb{D}} \newcommand{\F}{\mathbb{F}}
\newcommand{\N}{\mathbb{N}} \newcommand{\R}{\mathbb{R}}
\newcommand{\T}{\mathbb{T}} \newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}

@@

($\textbf{Collaboration}$ with Sharat, Harry and Logan)

@@

Pr(Y > 1+\epsilon) &= Pr(e^{tY}> e^{t(1+\epsilon)} )\\

@@

Fix some sink $s_i$. Let $T = \{t_j: (s_i,t_j) \text{ is a source-sink pair}\}$. We remove all edges incident to $s_i$ in the second phase of the algorithm when we do not delete all edges on some $s_i-t_j$ path for some $t_j \in T$. For all edges on some $s_i-t_j$ path to be preserved, necessarily $v_{s_i}$ and $v_{t_j}$ lie in the same region. Since $v_{s_i}$ and $v_{t_j}$ are orthogonal, by the constraints of the vector program, the angle between them is $\frac{\pi}{2}$. Hence the probability they are not separated by some $r_\ell$ is 
$$1- \frac{\pi}{2}\cdot \frac{1}{\pi} = \frac{1}{2}.$$
So the probability they not separated by any $r_\ell$ for $\ell \in [t]$ is

@@

Now $|T| \leq \Delta$ and so we have
$$Pr(\text{delete all edges on $s_i$}) \leq \sum_{t_j \in T}Pr(\text{$s_i-t_j$ path survives}) \leq \sum_{t_j \in T}\frac{1}{2^t} \leq \frac{\Delta}{2^t}$$

@@

Let $X$ be a random variable counting the number of edges removed. Let $X_{ij}^1$ be an indicator variable indicating that edge $ij \in E$ is removed in the first phase. Let $X_{s_i}^2$ be an indicator variable indicating that all edges incident to source $s_i$ are removed in the second phase. By linearity of expectation we have
$$E[X] = \sum_{ij \in E} Pr(X_{ij}^1) + \sum_{i \in [k]}Pr(X_{s_i}^2).$$
Now by $7c)$, $Pr(X_{s_i}^2) \leq \frac{\Delta}{2^t}$, so
$$ \sum_{i \in [k]}Pr(X_{s_i}^2) \leq k\frac{\Delta}{2^t} = k\Delta 2^{-\ceil{\log_2(\Delta /\epsilon)}} \leq k\epsilon \leq \epsilon |E|.$$
Thus
$$E[X] \leq \sum_{ij \in E} Pr(X_{ij}^1) + \epsilon |E|.$$
From $7b)$, $Pr(X_{ij}^1) \leq t\sqrt{1-v_i\cdot v_j}$, so we have
$$\sum_{ij \in E} Pr(X_{ij}^1) \leq t\sum_{ij \in E} \sqrt{1-v_i\cdot v_j}$$
Let $\mathbbm{1} \in \R^E$ be the vector of all ones. Let $q \in \R^E$ be the vector whose entries are defined by $q_{ij} = \sqrt{1-v_i\cdot v_j}$. Then 
$$\sum_{ij \in E} Pr(X_{ij}^1) \leq t \langle\mathbbm{1}, q_{ij} \rangle \leq t \sqrt{\langle \mathbbm{1}, \mathbbm{1}\rangle \langle q,q\rangle}$$
with the last inequality following from Cauchy-Schwarz. Now we see
$$\sqrt{\langle \mathbbm{1}, \mathbbm{1}\rangle \langle q,q\rangle} = \sqrt{|E|}\sqrt{\sum_{ij \in E} (1-v_i\cdot v_j)} = \sqrt{|E|}\sqrt{\epsilon |E|} = \sqrt{\epsilon}|E|$$
with the second equality following from the observation that $\sum_{ij \in E}(1-v_i\cdot v_j)$ is the objective function of the vector program. Hence, using the definition of $t$,
$$\sum_{ij \in E} Pr(X_{ij}^1) \leq t\sqrt{\epsilon}|E| = O(\log_2(\Delta/\epsilon)\sqrt{\epsilon}|E|)$$
$$E[X] \leq O(\log_2(\Delta/\epsilon)\sqrt{\epsilon}|E|) + \epsilon |E| = O (\sqrt{\epsilon}|E| + \sqrt{\epsilon}\log(\Delta/\epsilon)|E|)$$
